iterSim

### 2023-04-05 analyses/optimizeComplex.Rmd
File Changes

---
title: "iterSim"
output: html_document
params:
  epo: 200
  patience: 5
  iteration: 2
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta =0# 10^-7

@@

numSamp<-2000

baselineTrials<-2

@@

```{r complexPrep,eval=T}

@@

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*t+#*x[["z2"]]*
    #betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=0.05,z2=1.05,z3=1.05,term1=2.4,term3=1.05)#term2=1.05,

#########################
###Simulate data
#########################
cov<-data.frame(id=1:numSamp,
                z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5)))
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                     data = brcancer, k = 3
) #from flexsurv

dat <- simsurv(betas = coefficients, # "true" parameter values
               x = cov,                   # covariate data for 200 individuals
               knots = true_mod$knots,    # knot locations for splines
               logcumhazard = logcumhaz,  # definition of log cum hazard
               maxt = 25,               # no right-censoring
               interval = c(0,10000000)) # interval for root finding
colnames(dat)<-c("id","time","status")
samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
dat$status[samp]<-0
# Merge the simulated event times onto covariate data frame
data <- merge(cov, dat)
covs<-colnames(data)
data<-data[,-1]

toDiv<-max(data$time)
data$time<-data$time/toDiv
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"ComplexSimTest.rds")

k=5
klist<-list()
data<-res$train
for(i in 1:k){

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"ComplexSimCV.rds")

@@

```{r setFixedHyperparameters}

klist<-readRDS("ComplexSimCV.rds")
# lr=c(0.001,0.01)
# drpt=c(0.25,0.5)
# layer1=c(50,75,100)
# layer2=c(50,75)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","tanh")
# alp=c(0,0.5,1)

lr=c(0.001,0.0001)
drpt=c(.1,.2)
layer1=c(10,25,50)
layer2=c(10,20,30)
bsize=c(floor(nrow(klist[[1]]$train)/100))
actv=c("relu","tanh")
alp=c(0,0.5,1)

@@

```{r hyperOpDsurv,eval=T}

optimDeepSurv<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,bsize,actv){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             bsize=c(bsize),
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds)
      train<-normalizer(train,means,sds)

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=paramTrials[i,]$bsize
      actv=paramTrials[i,]$actv
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/optimDSurv.py')

      currentTime<-Sys.time() 
      coxnnsurv=fitDeepSurv(train,val,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
      tempVal<-append(tempVal,min(coxnnsurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      # coxnnsurv<-coxnnsurv[[1]]
      # coxnnsurv<-t(coxnnsurv)
      # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
      # cnnCleaned<-pyProcess(coxnnsurv,times=times)
      # colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
      # py_run_string("del fitDeepSurv")
      rm(fitDeepSurv)
      # brierFinalResults <- Score(list('ds'=cnnCleaned),
      #                            data =as.data.frame(val),#rbind(train,val) 
      #                            formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
      #                            se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
      # cutted<-brierFinalResults[which(brierFinalResults$model=="ds"),]
      #tempRes<-append(tempRes,mean(cutted[-c(1,2,24,25)]$IPA))
    }

@@

bestDS<-optimDeepSurv(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv)
```

```{r optimDeepHit,eval=T}

optimDeepHit<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,bsize,actv,alp){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             bsize=c(bsize),
                                             actv=actv,
                                             alp=alp,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds)
      train<-normalizer(train,means,sds)

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=paramTrials[i,]$bsize
      actv=paramTrials[i,]$actv
      alp=paramTrials[i,]$alp
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/optimDH.py')

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(mean(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

@@

bestDH<-optimDeepHit(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv,alp)

@@

```{r hyperopcbnn,eval=T}

optimCBNN<-function(klist,test,times,lr,drpt,layer1,layer2,bsize,actv){

@@

      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds)
      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=c(floor(nrow(train)/100))
      actv=paramTrials[i,]$actv

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      rm(cbnn,fit,covars_input,covars_output)
    }
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

@@

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,bsize,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]

@@

@@

saveRDS(winners,"complexOptimWins.rds")
```

```{r bestFits,finalFit}

@@

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1

@@

  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))

  fullTest<-readRDS("ComplexSimTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds)

  val<-normalizer(res$validate,means,sds)

  train<-normalizer(train,means,sds)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  valcb$offset<-0
  valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 27
  )

@@

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:time+z2:z3,#+z1:z3
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

@@

  #########################
  ###casebase+splines
  ##########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

@@

  lr=winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=winners$ds$bsize
  actv=winners$ds$actv

@@

  #############################
  ###DEEPHIT
  #############################
  lr=winners$dh$lr
  drpt=winners$dh$drpt
  layer1=winners$dh$layer1
  layer2=winners$dh$layer2
  bsize=winners$dh$bsize
  actv=winners$dh$actv
  alp=winners$dh$alp
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
  hitnnSurv<-t(hitnnSurv)
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-times
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

  #############################
  ###CBNN
  #############################
  train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
  val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                 as.matrix(valcb[,ncol(valcb),drop=F])),
            as.matrix(valcb[,ncol(valcb)-1,drop=F]))

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  #bsize=winners$cbnn$bsize
  actv=winners$cbnn$actv

  # lr=0.001
  # drpt=0.1
  # layer1=50
  # layer2=20
  # #bsize=winners$cbnn$bsize
  # actv='relu'

@@

  fit<-fitSmoothHaz(cbnn,
                    epochs=epo,
                    batch_size=c(floor(nrow(train)/100)),
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=val)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

numSamp<-5000

#baselineTrials<-2

@@

```{r complexPrep,eval=FALSE,hide=FALSE}

@@

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*t+
    #betas[["term2"]] * x[["z1"]]*x[["z2"]]*t*t+

    #betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
#url<-'app.txt'
#ds <- read.table(url, sep = '',header = TRUE)
#ds$years.at.risk=pmin(ds$agein80,ds$onset)
#brcancer$rectime<-brcancer$rectime
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
#coefficients<-c(coefficients,z1=-10,z2=1,z3=1,term1=0.005,term3=1)
coefficients<-c(coefficients,z1=-5,z2=-1,z3=1,term1=0.001,term3=-1)#z1 time interaction

#########################
###Simulate data
#########################
cov<-data.frame(id=1:numSamp,
                z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                z2=c(rnorm(numSamp/2,1,0.5),rnorm(numSamp/2,0,0.5)),
                z3=c(rnorm(numSamp,1,0.5)))

true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                     data = brcancer, k = 3
) #from flexsurv

dat <- simsurv(betas = coefficients, # "true" parameter values
               x = cov,                   # covariate data for 200 individuals
               knots = true_mod$knots,    # knot locations for splines
               logcumhazard = logcumhaz,  # definition of log cum hazard
               maxt = 10000,               # no right-censoring
               interval = c(0,100000000)) # interval for root finding
colnames(dat)<-c("id","time","status")
sum(dat$status)

samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
dat$status[samp]<-0
# Merge the simulated event times onto covariate data frame
data <- merge(cov, dat)

covs<-colnames(data)
data<-data[,-1]
hist(data$time[which(data$z1==0)],breaks=100)
hist(data$time[which(data$z1==1)],breaks=100)
median(data$time[which(data$z1==0)])
median(data$time[which(data$z1==1)])
#data$zsplit<-NULL
#toDiv<-max(data$time)
#data$time<-data$time/toDiv
spec = c(train = .85, test = .15)

@@

res = split(data, g)
#saveRDS(res$test,"ComplexSimTest.rds")

k=3
klist<-list()
data<-res$train
for(i in 1:k){

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"ComplexSimCV.rds")

@@

```{r setFixedHyperparameters,eval=FALSE,hide=FALSE}

klist<-readRDS("ComplexSimCV.rds")

# lr=c(0.001,0.01)
# drpt=c(0.1,0.25)
# layer1=c(25,50,100)
# layer2=c(25,50,100)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","tanh")#
# alp=c(0,0.5,1)

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)
# 
# lr=c(0.001)
# drpt=c(0.01)
# layer1=c(50)
# layer2=c(10)
# nBatch=c(100)
# actv=c("relu")#
# alp=c(0)

@@

```{r hyperOpDsurv,eval=FALSE,hide=FALSE}

optimDeepSurv<-function(klist,test,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/dsurv.py')

      ctrain<-train
      #ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

      coxnnsurv=fitDeepSurv(ctrain,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)

      coxnnsurv<-t(coxnnsurv)
      cnnCleaned<-pyProcess(coxnnsurv,times=times)
      colnames(cnnCleaned)<-times
      py_run_string("del fitDeepSurv")
      rm(fitDeepSurv)

      miniee <- Score(list('mod'=cnnCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      # coxnnsurv<-coxnnsurv[[1]]
      # coxnnsurv<-t(coxnnsurv)
      # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
      # cnnCleaned<-pyProcess(coxnnsurv,times=times)
      # colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
      # py_run_string("del fitDeepSurv")
      # rm(fitDeepSurv)
      # brierFinalResults <- Score(list('ds'=cnnCleaned),
      #                            data =as.data.frame(val),#rbind(train,val) 
      #                            formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
      #                            se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
      # cutted<-brierFinalResults[which(brierFinalResults$model=="ds"),]
      # tempRes<-append(tempRes,mean(cutted[-c(1,2,24,25)]$IPA))
    }

@@

bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

```{r optimDeepHit,eval=FALSE,hide=FALSE}

optimDeepHit<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             alp=alp,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      alp=paramTrials[i,]$alp
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/deephitter.py')
      hitnnSurv=fitDeephit(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      hitnnSurv<-t(hitnnSurv)
      deephitCleaned<-pyProcess(hitnnSurv,times=times)
      colnames(deephitCleaned)<-times
      py_run_string("del fitDeephit")
      rm(fitDeephit)

      miniee <- Score(list('mod'=deephitCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }

@@

bestDH<-optimDeepHit(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=FALSE,hide=FALSE}

optimCBNN<-function(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv){

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds,maxTime)

      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds,maxTime)
      valTest<-val
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))
      #val[[1]][[2]]<-rep(0,nrow(val[[1]][[1]]))

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=c(floor(nrow(train)/paramTrials[i,]$nBatch))
      actv=paramTrials[i,]$actv

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      #tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))
      annPreds<-aar(fit,
                    times=times,
                    x_test=valTest[,-c(ncol(valTest))]
      )

      rownames(annPreds)<-annPreds[,1]
      annProperpoly<- t(annPreds[,-1])
      class(annProperpoly)<-c("tunnel",class(annProperpoly))

      miniee <- Score(list('mod'=annProperpoly),
                      data =valTest, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])

      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      rm(cbnn,fit,covars_input,covars_output)
    }

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

@@

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv)

#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]

@@

```{r,eval=FALSE,hide=FALSE}

@@

#saveRDS(winners,"complexOptimWins.rds")
```

```{r bestFits,eval=T}

@@

start_time <- Sys.time()
BrierIPAList<-list()
AUClist<-list()
cScore<-list()
pos<-1

@@

  #train<-res$train
  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)

  fullTest<-readRDS("ComplexSimTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

  val<-normalizer(res$validate,means,sds,maxTime)

  train<-normalizer(train,means,sds,maxTime)
  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:time+ z2:z3,#+z1:z3
                                      data = linModelTrain,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

@@

  #########################
  ###casebase+splines
  ##########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = linModelTrain,
                                time = "time",
                                event="status",
                                ratio = 100
  )

@@

  lr=winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=ceiling(nrow(train)/winners$ds$nBatch)
  actv=winners$ds$actv

@@

  #############################
  ###DEEPHIT
  #############################
  lr=winners$dh$lr
  drpt=winners$dh$drpt
  layer1=winners$dh$layer1
  layer2=winners$dh$layer2
  bsize=ceiling(nrow(train)/winners$dh$nBatch)
  actv=winners$dh$actv
  alp=winners$dh$alp
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
  hitnnSurv<-t(hitnnSurv)
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-times
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ############################
  ###coxph
  ############################  
  cox<-coxph(Surv(time, status) ~ ., data = linModelTrain,x=T)

  #############################
  ###CBNN
  #############################
  tempTrain<-train
  train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
  valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
  val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                 as.matrix(valcb[,ncol(valcb),drop=F])),
            as.matrix(valcb[,ncol(valcb)-1,drop=F]))

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  bsize=c(floor(nrow(train)/winners$cbnn$nBatch))
  actv=winners$cbnn$actv

  #  lr=0.001
  #  drpt=0.1
  #  layer1=10
  #  layer2=10
  # bsize=c(floor(nrow(train)/100))# bsize=#winners$cbnn$bsize
  #  actv='relu'

@@

  fit<-fitSmoothHaz(cbnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=val)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )
